Crystal-amorphous interface induced by graphene nano-knot

### 2017-07-02 latex/paper.tex
basic text

% @Author: YangZhou
% @Date:   2017-06-20 20:27:38
% @Last Modified by:   YangZhou
% @Last Modified time: 2017-07-02 14:27:44
\documentclass[%
 reprint,
 amsmath,amssymb,
 aps,
prb,
]{revtex4-1}
\preprint{APS/123-QED}
\usepackage{graphicx}% Include figure files
\usepackage{bm}% bold math
\newcommand{\angstrom}{\mbox{\normalfont\AA}}
\begin{document}
\title{Crystal-amorphous interface induced by graphene nano-knot}
\author{Yang Zhou${}^{1,2}$}
\author{Zhi-Xin Guo${}^{3}$}
\author{Shi-you Chen}
\author{Hongjun Xiang}
\author{Xin-Gao Gong${}^{1,2}$}
\email{xggong@fudan.edu.cn}
\affiliation{%
  ${}^1$Key Laboratory for Computational Physical Science (Ministry of Education), State Key Laboratory of Surface Physics and Department of Physics, Fudan University, Shanghai 200433, China\\
  ${}^2$Collaborative Innovation Center of Advanced Microstructures, Nanjing 210093, Jiangsu, China\\
  ${}^3$Department of Physics, Xiangtan University, Xiangtan 411105, China
}%
\begin{abstract}
  Mechanical and thermal transport properties of graphene nanoribbon knots, are systematically investigated using nonequilibrium molecular dynamics. It is found that the thermal conductivity of the ribbon decreases largely due to the presence of the knots as a defect, but with the increasing of strain, the Kapitza resistance decreases, which is due to a tighter contacting of the ribbon with itself or the other. Local phonon analysis is applied to the contacting regime to reveal the influence of the contacts on the transport. This work would be helpful for a deeper understanding of thermal conducting at nanoscale and give a guidance to the field of phonon management material design.
  \begin{description}
    \item[Keywords]
          Thermal conductivity,graphene, knot , molecular dynamics ,amorphous
  \end{description}
\end{abstract}

@@

To have a global vision of the break process we carried out more analysis on the break data as shown in Fig.\ref{fig:drop}. From figure a) we found that the first drop happens at arount 0.2

@@

\begin{figure}[b]
  \includegraphics[width=\textwidth]{images/tc_lx}
  \caption{\label{fig:tc_lx}  (color online) The perspective view of a graphene knot}
\end{figure}

\begin{figure}[b]
  \includegraphics[width=\textwidth]{images/tc_nx}
  \caption{\label{fig:tc_nx}  (color online) The perspective view of a graphene knot}
\end{figure}

\begin{figure}[b]
  \includegraphics[width=\textwidth]{images/dos}
  \caption{\label{fig:dos}  (color online) The perspective view of a graphene knot}
\end{figure}

\section{CONCLUSIONS}

>>>>

% @Author: YangZhou
% @Date:   2017-06-20 20:27:38
% @Last Modified by:   YangZhou
% @Last Modified time: 2017-07-02 16:14:21
\documentclass[%
 reprint,
 amsmath,amssymb,
 aps,
prb,
]{revtex4-1}
\preprint{APS/123-QED}
\usepackage{graphicx}% Include figure files
\usepackage{bm}% bold math
\newcommand{\angstrom}{\mbox{\normalfont\AA}}
\begin{document}
\title{Crystal-amorphous interface induced by graphene nano-knot}
\author{Yang Zhou${}^{1,2}$}
\author{Zhi-Xin Guo${}^{3}$}
\author{Shi-you Chen}
\author{Hongjun Xiang}
\author{Xin-Gao Gong${}^{1,2}$}
\email{xggong@fudan.edu.cn}
\affiliation{%
  ${}^1$Key Laboratory for Computational Physical Science (Ministry of Education), State Key Laboratory of Surface Physics and Department of Physics, Fudan University, Shanghai 200433, China\\
  ${}^2$Collaborative Innovation Center of Advanced Microstructures, Nanjing 210093, Jiangsu, China\\
  ${}^3$Department of Physics, Xiangtan University, Xiangtan 411105, China
}%
\begin{abstract}
  Mechanical and thermal transport properties of graphene nanoribbon knots, are systematically investigated using nonequilibrium molecular dynamics. It is found that the thermal conductivity of the ribbon decreases largely due to the presence of the knots as a defect, but with the increasing of strain, the Kapitza resistance decreases, which is due to a tighter contacting of the ribbon with itself or the other. Local phonon analysis is applied to the contacting regime to reveal the influence of the contacts on the transport. This work would be helpful for a deeper understanding of thermal conducting at nanoscale and give a guidance to the field of phonon management material design.
  \begin{description}
    \item[Keywords]
          Thermal conductivity,graphene, knot , molecular dynamics ,amorphous
  \end{description}
\end{abstract}

@@

To have a global vision of the break process we carried out more analysis on the break data as shown in Fig.\ref{fig:drop}. From figure Fig.\ref{fig:drop}a we found that the first drop happens at around 7\%  and the distribution is pretty concentrate. While the second break happens when the strain is bwteen 10\% to 40\% and is obviously broaded. This state is unstable and could be either break right after the first break or hold for a large range of strain. The 3rd and 4th breaks happens almost at the same range and has a wider range.The Young's modules distribution of the states between all the break is shown in Fig.\ref{fig:drop}b. The value at aboutn $220GP/m$ present for the modules of unbreak knot and this value is much smaller than that of graphene ribbon of $900GP/m$. The rest of the modules exhibit a slow decrease from 0 to $300GP/m$ and most of them are below 150 $300GP/m$ ,which shows that the system is softer.Fig.\ref{fig:drop}c shows the probobility of total break times when considering strain in range 0 to 1.0. The distribution exhibit a long tail.  Most of the samples break down within two or three times while that of four to five also have relative big probability. In the extreme situation the system could break up to 9 times. Fig.\ref{fig:drop}d shows the the probability of break down. Below 0.07 there's no probability of breaking down and the structure is stable. when above 0.07 there's about 2\% samples break down. With the strain increase the system has larger probability to break down, however the probability increase slower and slower which is due to the softer feature of the filament and the same strain contributes lesser
stress so the lesser probability of break down. When the strain reaches about 0.9 all the samples must have broken down.

@@

Graphene exhibit excellent transport properties but the present of knot defect will largely reduce the value and it's unknown whether the stress affects the thermal transportation properties. Fig.\ref{fig:tc_lx} shows the
thermal conductivity versus strain of different length. The strain have ignorable influence on the thermal condcutivity. However the strain effect of graphene is very clear. This is because the strain is eliminated by the out-of-plane displacement which has little influence on the in-plane bond length.
\begin{figure}[b]
  \includegraphics[width=\textwidth]{images/tc_lx}
  \caption{\label{fig:tc_lx}  (color online) The perspective view of a graphene knot}
\end{figure}

At a large scale the knot superlattice could be regard as a particle-spring chain and we also studyed the thermal conductivity of the knot superlattice.
The TC of interface is  called Kapitza conductance and is shown in Fig.\ref{fig:tc_nx}a. TC increase with nx linearly and doesn't converge in the computational effort.Fig.\ref{fig:tc_nx}d shows the temperature profile of different nx. The position is normilzed to 1.0.With the increase of nx the profile converge to linear and the detail of the knot is no more important.
The total temperature drop at the knots are shown in Fig.\ref{fig:tc_nx}c. The total temperature drop increase when the number of knots increases because the temperature load on each of the ribbon decrease and the real temperature drop all concentrate on the knots. The average temperature drop of every knot is shown in Fig.\ref{fig:tc_nx}b. When nx is small dT is very large and with the increase of nx this value decrease a lot. This is obvious becasue the total temperature is constant but the number of knot increases.

\begin{figure}[b]
  \includegraphics[width=\textwidth]{images/tc_nx}
  \caption{\label{fig:tc_nx}  (color online) The position is normilzed to 1.0 }
\end{figure}

For a deeper understanding of the transport properties we calculate the phonon density of states of graphene nanoribbon,the knot region and the bulk rigion of the knot. The bulk rigion is far away from the knot and has the same structure with the GNR. However the DOS of bulk regioin is not like graphene but silimar to the knot region. This suggests that the present of the knot import a non-local influence to the structure.

\begin{figure}[b]
  \includegraphics[width=\textwidth]{images/dos}
  \caption{\label{fig:dos}  (color online) The position is normilzed to 1.0 }
\end{figure}

\section{CONCLUSIONS}
In this paper we simulated the mechanical properties and  thermal transport properties of graphene nano knot with nonequilibrium molecular dynamics(NEMD).
